What factors can affect COVID-19 results?

### 2022-04-26 inputs/data/datasheet_template.Rmd
:)

---
title: "Datasheet for the paper of analyzing the factors that may affect the COVID-19 results in Toronto"
author: 
  - Qingya Li
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

>>>>

---
title: "Datasheet for the paper of analyzing the factors that may affect the COVID-19 results in Toronto"
author: 
  - Qingya Li
thanks: "Code and data are available at: https://github.com/QingyaLi/What-factors-can-affect-COVID-19-results-"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

### 2022-04-26 outputs/paper/paper.Rmd
:)

thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The paper studied the COVID-19 cases in Toronto. By creating some visualizations and applying binomial regression models, we found outbreak-associated, age, gender,  infection source, classification type, ever hospitalized, ever in ICU, ever intubated are correlated to the recovery/fatality of the COVID-19 cases. It is necessary for us to conduct such research since it can provide a pathway for the prevention of the pandemic. \\par \\textbf {Keywords:} COVID-19, pandemic, Toronto, Toronto Open Data Portal, Canada"
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

>>>>

thanks: "Code and data are available at: https://github.com/QingyaLi/What-factors-can-affect-COVID-19-results-"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The paper studied the COVID-19 cases in Toronto. By creating some visualizations and applying binomial regression models, we found outbreak-associated, age, gender,  infection source, classification type, ever hospitalized, ever in ICU, ever intubated are correlated to the recovery/fatality of the COVID-19 cases. It is necessary for us to conduct such research since it can provide a pathway for the prevention of the pandemic. \\par \\textbf {Keywords:} COVID-19, pandemic, Toronto, Toronto Open Data Portal, Canada"
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---
